---
title: "Query Generation Robustness Analysis Report"
subtitle: "Systematic Evaluation of LLM-Based Query Variation Stability"
author: "Auto-SLR Research Team"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    theme: cosmo
    highlight: tango
    code_folding: hide
    number_sections: true
    fig_width: 12
    fig_height: 7
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center',
  dpi = 300
)

# Load required libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(jsonlite)
library(gridExtra)
library(scales)

# Set theme
theme_set(theme_minimal() + theme(
  plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(size = 11, hjust = 0.5),
  axis.title = element_text(size = 11, face = "bold"),
  legend.position = "right"
))
```

# Executive Summary {.unnumbered}

This report presents the findings from a comprehensive robustness test of our LLM-based query generation system. We generated 20 query variations from a single research question to evaluate the stability and sensitivity of the 4-agent pipeline (Pulse → Formulator → Sentinel → Refiner).

## Key Findings {.unnumbered}

::: {.alert .alert-danger}
**Critical Issue: High Instability Detected**

- **Coefficient of Variation: 378.6%** (Extremely high)
- **Result Range: 9 to 87,884 papers** (9,765:1 ratio)
- **One defective query** (Variation 2) retrieved 85% of all results due to missing domain constraints
:::

::: {.alert .alert-success}
**Recommended Action**

Use **Variation 1** (219 papers) as the primary query for Phase 2 metadata search execution. This variation demonstrates balanced coverage of all three mandatory concepts: interventions, health outcomes, and study designs.
:::

---

# Research Question

The following research prompt was used to generate all 20 query variations:

::: {.card .border-primary .mb-3}
<div class="card-header bg-primary text-white">
**Improved Research Prompt**
</div>
<div class="card-body">

I am interested in research papers that evaluate the causal impact of weather forecast-based interventions on the temperature-health relationship.

**INTERVENTION SCOPE:**

- Heat warning systems
- Heat-health action plans
- Cooling center programs triggered by heat forecasts
- Public health advisories based on weather predictions
- Other interventions activated by temperature forecasts

**STUDY DESIGN REQUIREMENTS:**

I specifically want studies with rigorous causal research designs that can isolate the impact of these interventions, including:

- Randomized controlled trials (RCTs)
- Quasi-experimental designs (difference-in-differences, regression discontinuity, interrupted time series)
- Natural experiments
- Instrumental variable approaches

**OUTCOMES OF INTEREST:**

- Temperature-related mortality
- Heat-related morbidity (hospitalizations, emergency department visits)
- Cardiovascular and respiratory health impacts during heat events

**SCOPE:**

- Papers from any country or population
- Any time period
- Both observational causal designs and experimental studies

</div>
:::

---

# Test Configuration

```{r load-data}
# Load search results data
results_list <- list()
search_results_dir <- "search_results"

for (var_dir in list.dirs(search_results_dir, recursive = FALSE)) {
  var_num <- as.integer(sub(".*variation_(\\d+)", "\\1", basename(var_dir)))
  summary_file <- file.path(var_dir, "openalex", "run_summary.json")

  if (file.exists(summary_file)) {
    data <- fromJSON(summary_file)
    results_list[[length(results_list) + 1]] <- data.frame(
      variation = var_num,
      papers = data$meta_count,
      results_count = data$results_count,
      status = data$status
    )
  }
}

results_df <- bind_rows(results_list) %>% arrange(variation)

# Calculate statistics
stats <- results_df %>%
  summarise(
    n = n(),
    min = min(papers),
    max = max(papers),
    mean = mean(papers),
    median = median(papers),
    sd = sd(papers),
    cv = (sd / mean) * 100,
    range = max - min,
    ratio = max / min
  )
```

## Methodology

- **Number of Variations**: 20
- **Database**: OpenAlex only (for efficiency and comprehensive coverage)
- **Query Generation**: AWS Bedrock (Claude Sonnet 4.6)
- **Max Results**: Unlimited (downloaded all matching papers per variation)
- **Metadata Saved**: DOI + OpenAlex ID only (minimal footprint)
- **Execution Time**: ~50 minutes total

## Pipeline Architecture

```
Research Question → Pulse Agent (Keywords) → Formulator Agent (Boolean Queries)
                   ↓
    Refiner Agent (Final Polish) ← Sentinel Agent (Quality Check)
                   ↓
    OpenAlex Search → Sensitivity Analysis
```

Each variation uses a different `variation_seed` parameter to introduce controlled randomness in keyword selection and query structure.

---

# Results Overview

## Statistical Summary

```{r stats-table}
stats_table <- data.frame(
  Metric = c("Coefficient of Variation", "Minimum Results", "Maximum Results",
             "Mean", "Median", "Standard Deviation", "Range", "Ratio (Max/Min)"),
  Value = c(
    paste0(round(stats$cv, 1), "%"),
    paste0(stats$min, " papers (Variation 8)"),
    paste0(format(stats$max, big.mark = ","), " papers (Variation 2)"),
    paste0(format(round(stats$mean), big.mark = ","), " papers"),
    paste0(format(stats$median, big.mark = ","), " papers"),
    paste0(format(round(stats$sd), big.mark = ","), " papers"),
    paste0(format(stats$range, big.mark = ","), " papers"),
    paste0(format(round(stats$ratio), big.mark = ","), ":1")
  )
)

kable(stats_table, col.names = c("Metric", "Value"),
      caption = "Statistical Summary of Query Robustness Test") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  row_spec(1, bold = TRUE, background = "#FFC7CE")  # Highlight CV
```

## Result Distribution {.tabset}

### Linear Scale

```{r fig1-distribution, fig.width=14, fig.height=7}
results_df <- results_df %>%
  mutate(
    category = case_when(
      papers < 100 ~ "Too Narrow (<100)",
      papers <= 1500 ~ "Good (100-1,500)",
      papers <= 5000 ~ "Acceptable (1,500-5,000)",
      TRUE ~ "Too Broad (>5,000)"
    ),
    category = factor(category, levels = c("Too Narrow (<100)", "Good (100-1,500)",
                                            "Acceptable (1,500-5,000)", "Too Broad (>5,000)")),
    recommended = ifelse(variation == 1, "Variation 1 (Recommended)", "Other")
  )

color_map <- c(
  "Too Narrow (<100)" = "#e74c3c",
  "Good (100-1,500)" = "#27ae60",
  "Acceptable (1,500-5,000)" = "#f39c12",
  "Too Broad (>5,000)" = "#c0392b"
)

ggplot(results_df, aes(x = factor(variation), y = papers, fill = category)) +
  geom_bar(stat = "identity", color = "black", size = 1) +
  geom_bar(data = filter(results_df, variation == 1),
           aes(x = factor(variation), y = papers),
           stat = "identity", fill = "#27ae60", color = "#2980b9", size = 2) +
  geom_text(aes(label = format(papers, big.mark = ",")),
            vjust = -0.5, size = 3, fontface = "bold") +
  scale_fill_manual(values = color_map, name = "Quality Category") +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.1))) +
  labs(
    title = "Query Robustness Test: Result Distribution Across 20 Variations",
    x = "Variation Number",
    y = "Number of Papers Retrieved"
  ) +
  theme(axis.text.x = element_text(angle = 0))
```

### Log Scale

```{r fig2-distribution-log, fig.width=14, fig.height=7}
ggplot(results_df, aes(x = factor(variation), y = papers, fill = category)) +
  geom_bar(stat = "identity", color = "black", size = 1) +
  geom_bar(data = filter(results_df, variation == 1),
           aes(x = factor(variation), y = papers),
           stat = "identity", fill = "#27ae60", color = "#2980b9", size = 2) +
  scale_fill_manual(values = color_map, name = "Quality Category") +
  scale_y_log10(labels = comma, breaks = c(10, 100, 1000, 10000, 100000)) +
  annotate("segment", x = 2, xend = 2, y = 87884, yend = 70000,
           arrow = arrow(length = unit(0.3, "cm")), color = "red", size = 1) +
  annotate("label", x = 5, y = 50000,
           label = "Var 2: 87,884 papers\n(DEFECT: Missing health terms)",
           fill = "yellow", color = "red", fontface = "bold", size = 3.5) +
  annotate("segment", x = 1, xend = 1, y = 219, yend = 150,
           arrow = arrow(length = unit(0.3, "cm")), color = "#2980b9", size = 1) +
  annotate("label", x = 4, y = 150,
           label = "Var 1: 219 papers\n(RECOMMENDED)",
           fill = "lightblue", color = "#2980b9", fontface = "bold", size = 3.5) +
  labs(
    title = "Query Robustness Test: Result Distribution (Log Scale)",
    x = "Variation Number",
    y = "Number of Papers (Log Scale)"
  ) +
  theme(axis.text.x = element_text(angle = 0))
```

### Distribution Details

```{r distribution-table}
results_summary <- results_df %>%
  arrange(papers) %>%
  mutate(
    Status = case_when(
      papers < 100 ~ "❌ TOO NARROW",
      papers <= 1500 ~ "✅ EXCELLENT/GOOD",
      papers <= 5000 ~ "⚠️ ACCEPTABLE",
      TRUE ~ "❌ TOO BROAD"
    )
  ) %>%
  select(Variation = variation, Papers = papers, Status)

kable(results_summary, format.args = list(big.mark = ","),
      caption = "Result Distribution by Variation (Sorted by Paper Count)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(which(results_summary$Variation == 1), bold = TRUE, background = "#d4edda") %>%
  row_spec(which(results_summary$Variation == 2), bold = TRUE, background = "#f8d7da")
```

---

# Statistical Analysis {.tabset}

## Multi-Panel Summary

```{r fig3-stats, fig.width=14, fig.height=10}
# Prepare plots
p1 <- ggplot(results_df, aes(x = "", y = papers)) +
  geom_boxplot(fill = "lightblue", alpha = 0.7) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3, fill = "red") +
  scale_y_continuous(labels = comma) +
  labs(title = "A. Box Plot (Showing Outliers)",
       x = "", y = "Number of Papers") +
  annotate("text", x = 1.3, y = stats$max * 0.7,
           label = sprintf("Min: %s\nQ1: %s\nMedian: %s\nQ3: %s\nMax: %s",
                          format(stats$min, big.mark = ","),
                          format(round(quantile(results_df$papers, 0.25)), big.mark = ","),
                          format(stats$median, big.mark = ","),
                          format(round(quantile(results_df$papers, 0.75)), big.mark = ","),
                          format(stats$max, big.mark = ",")),
           hjust = 0, size = 3)

p2 <- ggplot(results_df, aes(x = papers)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black", alpha = 0.7) +
  geom_vline(xintercept = stats$mean, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = stats$median, color = "green", linetype = "dashed", size = 1) +
  scale_x_continuous(labels = comma) +
  labs(title = "B. Distribution Histogram",
       x = "Number of Papers", y = "Frequency") +
  annotate("text", x = stats$mean, y = Inf,
           label = paste("Mean:", format(round(stats$mean), big.mark = ",")),
           vjust = 2, color = "red", fontface = "bold", size = 3) +
  annotate("text", x = stats$median, y = Inf,
           label = paste("Median:", format(stats$median, big.mark = ",")),
           vjust = 4, color = "green", fontface = "bold", size = 3)

p3 <- results_df %>%
  count(category) %>%
  ggplot(aes(x = "", y = n, fill = category)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y") +
  scale_fill_manual(values = color_map) +
  geom_text(aes(label = paste0(n, "\n(", round(n/20*100), "%)")),
            position = position_stack(vjust = 0.5), fontface = "bold") +
  labs(title = "D. Quality Distribution", fill = "Category") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

# Combine plots
grid.arrange(p1, p2, p3, ncol = 2,
             top = "Statistical Summary: Multiple Perspectives")
```

## Detailed Statistics

```{r detailed-stats-table}
detailed_stats <- data.frame(
  Metric = c("Number of Variations", "Minimum", "Maximum", "Mean", "Median",
             "Standard Deviation", "Coefficient of Variation", "Range", "Ratio (Max/Min)",
             "Q1 (25th percentile)", "Q3 (75th percentile)", "IQR"),
  Value = c(
    "20",
    paste0(stats$min, " papers"),
    paste0(format(stats$max, big.mark = ","), " papers"),
    paste0(format(round(stats$mean), big.mark = ","), " papers"),
    paste0(format(stats$median, big.mark = ","), " papers"),
    paste0(format(round(stats$sd), big.mark = ","), " papers"),
    paste0(round(stats$cv, 1), "%"),
    paste0(format(stats$range, big.mark = ","), " papers"),
    paste0(format(round(stats$ratio), big.mark = ","), ":1"),
    paste0(format(round(quantile(results_df$papers, 0.25)), big.mark = ","), " papers"),
    paste0(format(round(quantile(results_df$papers, 0.75)), big.mark = ","), " papers"),
    paste0(format(round(IQR(results_df$papers)), big.mark = ","), " papers")
  )
)

kable(detailed_stats, col.names = c("Metric", "Value"),
      caption = "Comprehensive Statistical Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  row_spec(7, bold = TRUE, background = "#FFC7CE")  # Highlight CV
```

---

# Critical Issue Analysis

## Variation 2 Defect: The 87,884 Paper Problem

### Problem Description

Variation 2 retrieved **87,884 papers** (85% of all retrieved papers, 97.5% above the mean), creating a massive outlier that skews all statistics.

### Comparison: Variation 1 vs Variation 2

```{r fig5-comparison, fig.width=12, fig.height=6}
comparison_df <- results_df %>%
  filter(variation %in% c(1, 2)) %>%
  mutate(
    label = case_when(
      variation == 1 ~ "Variation 1\n(RECOMMENDED)",
      variation == 2 ~ "Variation 2\n(DEFECTIVE)"
    ),
    color = ifelse(variation == 1, "#27ae60", "#c0392b")
  )

ggplot(comparison_df, aes(x = label, y = papers, fill = color)) +
  geom_bar(stat = "identity", color = "black", size = 1.5, width = 0.6) +
  geom_text(aes(label = format(papers, big.mark = ",")),
            vjust = -0.5, size = 6, fontface = "bold") +
  scale_fill_identity() +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.1))) +
  annotate("segment", x = 1, xend = 1, y = 219, yend = 15000,
           arrow = arrow(length = unit(0.4, "cm")), color = "green", size = 1.2) +
  annotate("label", x = 0.7, y = 20000,
           label = "Balanced query:\n✓ Interventions\n✓ Outcomes\n✓ Methods",
           fill = "lightgreen", color = "darkgreen", fontface = "bold", size = 4) +
  annotate("segment", x = 2, xend = 2, y = 87884, yend = 60000,
           arrow = arrow(length = unit(0.4, "cm")), color = "red", size = 1.2) +
  annotate("label", x = 1.7, y = 55000,
           label = "Missing constraints:\n✗ No interventions\n✗ No outcomes\n✓ Only methods",
           fill = "#ffcccc", color = "red", fontface = "bold", size = 4) +
  labs(
    title = "Critical Comparison: Variation 1 vs Variation 2",
    subtitle = sprintf("401× Difference (%.1f%% vs %.1f%% of total)",
                       219/sum(results_df$papers)*100,
                       87884/sum(results_df$papers)*100),
    x = NULL,
    y = "Number of Papers Retrieved"
  ) +
  theme(legend.position = "none")
```

### Root Cause

::: {.alert .alert-warning}
**Missing Domain Constraints**

The query for Variation 2 **completely lacks health intervention terms**:

**What it includes:**
- ✅ Methodology terms: "causal inference", "quasi-experimental", "natural experiment"
- ✅ Statistical methods: "difference-in-differences", "regression discontinuity"
- ✅ Evaluation terms: "policy evaluation", "program evaluation"

**What it's missing:**
- ❌ Heat warning system
- ❌ Heat mortality
- ❌ Cooling center
- ❌ Temperature-health
- ❌ Heat-related morbidity
- ❌ ANY health/climate intervention terms

**Consequence:** Retrieved **all causal inference papers** across all disciplines (economics, education, environmental science, etc.) instead of just heat-health interventions.
:::

---

# Sensitivity Analysis

```{r load-impact-data}
impact_df <- read.csv("analysis/openalex/impact_rankings.csv")

top_expanding <- impact_df %>%
  filter(impact_type == "EXPANDS") %>%
  arrange(desc(delta)) %>%
  head(10)

top_restricting <- impact_df %>%
  filter(impact_type == "RESTRICTS") %>%
  arrange(delta) %>%
  head(10)
```

## Term Impact Rankings {.tabset}

### Expanding Terms

```{r fig4-expanding, fig.width=14, fig.height=7}
top_expanding %>%
  mutate(term = reorder(term, delta)) %>%
  ggplot(aes(x = term, y = delta)) +
  geom_bar(stat = "identity", fill = "#e74c3c", color = "black", size = 1) +
  geom_text(aes(label = sprintf("+%s\n(+%.0f%%)",
                                format(delta, big.mark = ","),
                                percent_change)),
            hjust = -0.1, size = 3, fontface = "bold") +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(
    title = "Top 10 EXPANDING Terms",
    subtitle = "Dramatically Increase Results (Should Be Used WITH Domain Constraints)",
    x = NULL,
    y = "Increase in Papers"
  )
```

### Restricting Terms

```{r fig4-restricting, fig.width=14, fig.height=7}
top_restricting %>%
  mutate(term = reorder(term, abs(delta))) %>%
  ggplot(aes(x = term, y = abs(delta))) +
  geom_bar(stat = "identity", fill = "#27ae60", color = "black", size = 1) +
  geom_text(aes(label = sprintf("%s\n(%.1f%%)",
                                format(delta, big.mark = ","),
                                percent_change)),
            hjust = -0.1, size = 3, fontface = "bold") +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(
    title = "Top 10 RESTRICTING Terms",
    subtitle = "Effectively Narrow Results to Target Domain",
    x = NULL,
    y = "Decrease in Papers"
  )
```

### Impact Summary

```{r impact-tables}
# Expanding terms table
kable(top_expanding %>% select(Term = term, Impact = delta, `% Change` = percent_change),
      format.args = list(big.mark = ","),
      caption = "Top 10 Terms That EXPAND Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  row_spec(0, background = "#e74c3c", color = "white", bold = TRUE)

# Restricting terms table
kable(top_restricting %>% select(Term = term, Impact = delta, `% Change` = percent_change),
      format.args = list(big.mark = ","),
      caption = "Top 10 Terms That RESTRICT Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  row_spec(0, background = "#27ae60", color = "white", bold = TRUE)
```

---

# Root Cause Analysis

## Why Did This Happen?

### 1. LLM Keyword Expansion Instability

The **Pulse Agent** (keyword expansion) demonstrates high variability:

- ✅ **Strengths**: Generates diverse synonyms
- ❌ **Weakness**: Sometimes focuses on one concept while neglecting others
- ❌ **Critical Flaw**: No enforcement for balanced coverage

### 2. Sentinel Agent Quality Control Gap

The **Sentinel Agent** failed to detect missing concepts:

- ✅ **What it checks**: Boolean syntax, database formatting
- ❌ **What it missed**: Conceptual completeness
- ❌ **Gap**: No validation of mandatory concept coverage

### 3. Refiner Agent Correction Failure

The **Refiner Agent** did not add missing terms:

- ✅ **What it does**: Resolve flagged syntax issues
- ❌ **What it should have done**: Independent concept audit
- ❌ **Limitation**: Only fixes explicitly flagged issues

---

# Recommendations

## Immediate Actions (This Week)

::: {.alert .alert-success}
### 1. Use Variation 1 for Phase 2 Execution

**Query to use:** Variation 1
**Expected recall:** ~219 papers from OpenAlex
**Rationale:** Balanced coverage, reasonable result count

**Next step:** Extract OpenAlex query from `queries/variation_01_queries.json` → Phase 2 (metadata search) → Phase 3 (full-text retrieval) → Phase 4 (Claude screening)
:::

### 2. Alternative: Ensemble Strategy

Combine multiple high-quality variations:

- **Variations:** 1, 4, 6, 9, 16, 18, 20
- **Expected unique papers:** ~1,200-1,500 (after deduplication)
- **Method:** Union all DOIs, deduplicate

## Medium-term Improvements (1-2 Weeks)

### 3. Restructure the Research Prompt

Add **MANDATORY CONCEPTS** section:

```
MANDATORY CONCEPTS (ALL must be included in EVERY query):

1. INTERVENTION TERMS (minimum 3 required):
   - Heat warning systems, heat-health action plans, cooling centers, etc.

2. OUTCOME TERMS (minimum 3 required):
   - Temperature-related mortality, heat-related morbidity, etc.

3. STUDY DESIGN TERMS (minimum 2 required):
   - RCT, quasi-experimental, natural experiments, etc.
```

### 4. Enhance Sentinel Agent Validation

Implement concept coverage audit that flags missing concept groups as CRITICAL ERROR.

### 5. Re-run Test with Improved Prompt

**Goal:** Reduce CV from 378.6% to **< 50%**

## Long-term Strategy (1+ Month)

### 6. Hybrid Approach

- **Step 1:** Define minimum required term set (5-7 core terms per concept)
- **Step 2:** Pulse expands with synonyms
- **Step 3:** Sentinel verifies core terms 100% present
- **Step 4:** Refiner optimizes while preserving core terms

---

# Conclusions

## Summary of Findings

1. **High Instability Confirmed**: CV = 378.6% - system not production-ready
2. **Root Cause Identified**: Unstable keyword expansion + missing quality controls
3. **One Critical Defect**: Variation 2 demonstrates catastrophic failure mode
4. **Term Sensitivity Quantified**: Generic terms expand, specific terms restrict
5. **Solution Exists**: Mandatory concept constraints + enhanced validation

## Implications

### Short-term Path Forward

- **DO use:** Variation 1 (219 papers)
- **DO NOT use:** Variation 2 (87,884 papers)
- **Confidence:** Variation 1 is well-constructed and representative

### Medium-term System Improvement

- **Priority:** Implement mandatory concept coverage
- **Timeline:** 1-2 weeks for prompt + Sentinel enhancement
- **Validation:** Re-run test, target CV < 50%

---

# Appendices

## Appendix A: Variation 1 Query (Recommended)

```{r variation-1-query}
var1_file <- "queries/variation_01_queries.json"
if (file.exists(var1_file)) {
  var1 <- fromJSON(var1_file)
  cat("### OpenAlex Query:\n\n")
  cat("```\n")
  cat(var1$refiner_queries$openalex_query)
  cat("\n```\n\n")

  cat("### Concept Coverage:\n\n")
  cat(sprintf("- ✅ **Interventions**: %d terms\n",
              length(grep("heat|cooling|warning|action", unlist(strsplit(var1$pulse_keywords, " "))))))
  cat(sprintf("- ✅ **Outcomes**: %d terms\n",
              length(grep("mortality|morbidity|hospital|death|cardiovascular", unlist(strsplit(var1$pulse_keywords, " "))))))
  cat(sprintf("- ✅ **Methods**: %d terms\n",
              length(grep("quasi|experimental|causal|RCT|difference", unlist(strsplit(var1$pulse_keywords, " "))))))
}
```

## Appendix B: All 20 Variations Summary

```{r all-variations-table}
# Create summary table
variation_summary <- results_df %>%
  select(Variation = variation, `Paper Count` = papers, Category = category) %>%
  mutate(
    Assessment = case_when(
      `Paper Count` < 100 ~ "Too Narrow",
      `Paper Count` <= 1500 ~ "Excellent/Good",
      `Paper Count` <= 5000 ~ "Acceptable",
      TRUE ~ "Too Broad/Defective"
    )
  )

kable(variation_summary, format.args = list(big.mark = ","),
      caption = "Summary of All 20 Query Variations") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(which(variation_summary$Variation == 1),
           bold = TRUE, background = "#d4edda") %>%
  row_spec(which(variation_summary$Variation == 2),
           bold = TRUE, background = "#f8d7da")
```

## Appendix C: Technical Details

**Test Environment:**

- Platform: macOS (Darwin 25.3.0)
- Python: 3.11+ with virtual environment
- LLM Provider: AWS Bedrock (us-east-1)
- Model: Claude Sonnet 4.6
- Database: OpenAlex (API v1)

**Data Files:**

All raw data available in:
```
robustness_testing/results/20260325_194108_complete/
├── queries/                  # 20 query JSON files
├── search_results/           # 20 search result directories
└── analysis/openalex/        # Sensitivity analysis outputs
```

**Reproducibility:**

```bash
cd robustness_testing
python test_robustness_20runs.py \
  --num-variations 20 \
  --databases openalex \
  --llm-provider bedrock \
  --max-results 999999
```

---

::: {.alert .alert-info}
**Report Generated:** `r Sys.Date()`
**Test ID:** 20260325_194108_complete
**Total Variations:** 20
**Database:** OpenAlex
**Analysis Tool:** R + ggplot2 + knitr
:::

<style>
.alert {
  padding: 15px;
  margin-bottom: 20px;
  border: 1px solid transparent;
  border-radius: 4px;
}
.alert-danger {
  color: #721c24;
  background-color: #f8d7da;
  border-color: #f5c6cb;
}
.alert-success {
  color: #155724;
  background-color: #d4edda;
  border-color: #c3e6cb;
}
.alert-warning {
  color: #856404;
  background-color: #fff3cd;
  border-color: #ffeaa7;
}
.alert-info {
  color: #004085;
  background-color: #d1ecf1;
  border-color: #bee5eb;
}
.card {
  border: 1px solid rgba(0,0,0,.125);
  border-radius: .25rem;
}
.card-header {
  padding: .75rem 1.25rem;
  margin-bottom: 0;
  background-color: rgba(0,0,0,.03);
  border-bottom: 1px solid rgba(0,0,0,.125);
}
.card-body {
  padding: 1.25rem;
}
</style>
